Electrifying a Bus Network

### 2022-12-13 project/Paper.Rmd
update paper outline

---
title: Electrification of Bus Networks in Provo, Utah (DRAFT)
author: Hayden Atchley
date: "22 November 2022"
documentclass: article
geometry:
  - letterpaper
  - margin=1in
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    toc: false
    number_sections: false
header-includes:
  - \usepackage{setspace}
mainfont: Gentium Book Basic
bibliography: references.bib
---

>>>>

---
title: "Electrifying a Bus Network"
subtitle: "A UVX Case Study"
author: Hayden Atchley
date: "22 November 2022"
documentclass: article
geometry:
  - letterpaper
  - margin=1in
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    toc: false
    number_sections: false
header-includes:
  - \usepackage{setspace}
mainfont: Gentium Book Basic
bibliography: references.bib
---
